### 2016-08-11 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated event times and generated new data sets for gas burner tests

\subsection{Tests~22 \& 23}
Tests~22 and 23 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of both double doors was used during the tests to change the ventilation pattern within the structure.
\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	~(1)~  All burners on 						&   0	  			&	 0			\\
	~(2)~  2nd floor west double door opened 	&   194		  		&    130		\\
	~(3)~  1st floor west double door opened 	&	314		  		&    252 	 	\\
	~(4)~  1st floor east double door opened 	&   450			  	&    371		\\
	~(5)~  2nd floor east double door opened	&   585			  	&    498		\\
	~(6)~  PPV fan on 							&   652			  	&    612		\\
	~(7)~  PPV fan off              			&   798			  	&    761		\\
	~(8)~  All burners off 						&   829			  	&    794		\\
	~(9)~  2nd floor south exterior door opened &   899			  	&    849		\\
	(10) PPV fan on 	 						&   1065		  	&    940		\\
	(11) 2nd floor south exterior door closed   &   1176		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\subsection{Tests~24 \& 25}
Similar to Tests~22 and 23, Tests~24 and 25 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times corresponding to the data files for Tests~24 and 25. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the west double door was used during the tests to change the ventilation pattern within the structure.

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	~(1)~ All burners on 						&   0		  		&	 0			\\
	~(2)~ Interior stairwell door opened 		&   144		  		&    112		\\
	~(3)~ 1st floor west double door opened 	&	265		  		&    244 	 	\\
	~(4)~ 2nd floor west double door opened 	&   383			  	&    353		\\
	~(5)~ 2nd floor south exterior door opened	&   502			  	&    474		\\
	~(6)~ PPV fan on 							&   624			  	&    594 		\\
	~(7)~ All burners off 						&   746 		  	&    721		\\
	~(8)~ 2nd floor east double door opened 	&   877			  	&    N/A		\\
	~(9)~ 1st floor east double door opened		& 	N/A 			& 	 836		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.97\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\clearpage

>>>>

\subsection{Tests~22 \& 23}
Tests~22 and 23 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the two doors was used during the tests to change the ventilation pattern within the structure.
\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	~(1)~  All burners on 						&   0	  			&	 0			\\
	~(2)~  2nd floor west double door opened 	&   194		  		&    130		\\
	~(3)~  1st floor west double door opened 	&	314		  		&    252 	 	\\
	~(4)~  1st floor east double door opened 	&   450			  	&    371		\\
	~(5)~  2nd floor south exterior door closed &   511		  		&    N/A		\\
	~(6)~  2nd floor east double door opened	&   585			  	&    498		\\
	~(7)~  PPV fan on 							&   652			  	&    612		\\
	~(8)~  PPV fan off              			&   798			  	&    761		\\
	~(9)~  All burners off 						&   829			  	&    794		\\
	(10)   2nd floor south exterior door opened &   899			  	&    849		\\
	(11)   PPV fan on 	 						&   1065		  	&    940		\\
	(12)   2nd floor south exterior door closed &   1176		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\subsection{Tests~24 \& 25}
Similar to Tests~22 and 23, Tests~24 and 25 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times corresponding to the data files for Tests~24 and 25. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the west double door was used during the tests to change the ventilation pattern within the structure. Also, the stairwell door was unable to completely close. So, when it was in the ``closed'' position at the beginning of the tests, there was a 152~mm (6~in) gap between the door and its frame.

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	~(1)~ All burners on 						&   0		  		&	 0			\\
	~(2)~ Interior stairwell door opened 		&   144		  		&    112		\\
	~(3)~ 1st floor west double door opened 	&	265		  		&    244 	 	\\
	~(4)~ 2nd floor west double door opened 	&   383			  	&    353		\\
	~(5)~ 2nd floor south exterior door closed	&   452			  	&    N/A		\\
	~(6)~ 2nd floor south exterior door opened	&   502			  	&    474		\\
	~(7)~ PPV fan on 							&   624			  	&    594 		\\
	~(8)~ All burners off 						&   746 		  	&    721		\\
	~(9)~ 2nd floor east double door opened 	&   877			  	&    N/A		\\
	(10)  1st floor east double door opened		& 	N/A 			& 	 836		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.97\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\clearpage
